Individual ABC Fits

### 2024-01-29 Model/abc_reject.qmd
bring settings back down

future::plan(multisession)
k2 <- k |> mutate(pp=future_pmap(list(id,Model,Fit_Method,data), ~{
  generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 50, return_dat="test_data")
  }))

@@

@@

>>>>

future::plan(multisession)
# k2 <- k |> mutate(pp=future_pmap(list(id,Model,Fit_Method,data), ~{
#   generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = as.numeric(nrow(..4)), return_dat="test_data")
#   })) |> select(-data)

future::plan(multisession)
k2 <- k |> mutate(pp=furrr::future_pmap(list(id,Model,Fit_Method,data), ~{
  generate_data(..2, ..4 |> mutate(id=..1), ds, num_samples = 100), return_dat="test_data")
  })) |> select(-data)

# p <- k |>  mutate(n=future_pmap(list(id,Model,Fit_Method,data), ~{
#    as.numeric(nrow(..4))
#   }))

@@

##  Posterior Average Table: 
```{r fig.width=12, fig.height=17}
#| eval: true
post_tabs <- abc_tables(post_dat_l)
post_tabs$et_sum |> gt::gt()

post_tabs$et_sum |> select(condit,Fit_Method,Avg_ALM_error, Avg_EXAM_error) |> filter(Fit_Method=="Test")

 abc_tables(post_dat_l |> filter(rank<=100))$et_sum |> gt::gt()

 post_dat_l |> group_by(condit,Model,Fit_Method,rank) |> summarise(mean_error=mean(mean_error), n=n()) |> 
   ggplot(aes(x=rank,y=mean_error,fill=Model))+geom_col()+facet_wrap(~Fit_Method)

@@

### Subject 1
```{r fig.width=11, fig.height=12}

indv_predictive_dist((post_dat_l |> filter(rank<=200)),ind_fits_df2, sbj=list(1))
# plot_indv_posterior(ind_fits_df |> filter(id==1))
# ind_fits_df |> filter(id==1, Fit_Method=="Test Only", Model=="EXAM") |> pull(c) |> unique()

### Subject 36
```{r fig.width=11, fig.height=12}

indv_predictive_dist(post_dat_l,ind_fits_df2, sbj=list(36))
# plot_indv_posterior(ind_fits_df |> filter(id==1))
# ind_fits_df |> filter(id==1, Fit_Method=="Test Only", Model=="EXAM") |> pull(c) |> unique()
```

```{r fig.width=11, fig.height=8}

get_order_pattern <- function(df, pred_col = "pred",band_tol=50) {

  df <- df[order(df$x), ]
  # Calculate the standard deviation and determine the pattern
  pred_sd <- sd(df[[pred_col]]) / 2.8
  pattern <- ""
  # Iterate through the rows to build the pattern
  for (i in 1:(nrow(df) - 1)) {
    if (abs(df[[pred_col]][i] - df[[pred_col]][i + 1]) <= band_tol) {
      pattern <- paste0(pattern, "=")
    } else if (df[[pred_col]][i] < df[[pred_col]][i + 1]) {
      pattern <- paste0(pattern, "<")
    } else {
      pattern <- paste0(pattern, ">")
    }
  }

  return(pattern)
}

ind_ds <- ds |> 
  filter(expMode2 == "Test") |> 
  group_by(id, condit, x, expMode2) |> 
  summarise(y = mean(y), .groups = "keep")

# Apply the function to the dataset
ind_pattern <- ind_ds |> 
  group_by(id, condit, expMode2) |>
  do(order_pattern = get_order_pattern(., pred_col = "y",band_tol=50))

ind_ds <- ind_ds |>
  left_join(ind_pattern, by=join_by(id,condit,expMode2)) |> 
  mutate(order_pattern = unlist(order_pattern))

lorder <- ind_ds |>
  group_by(order_pattern, x) |>
  summarize(y = mean(y), n_id = n_distinct(id)) %>% 
  pull(n_id) %>% 
  unique() %>% 
  sort(decreasing = TRUE)

ord_pattern <- k3  |> filter(rank<=1) |>
  filter(expMode2=="Test") |> 
  group_by(condit,rank,Model,Fit_Method) %>% 
  do(order_pattern = unlist(get_order_pattern(.)))

combo_pred <- k3 |>  filter(rank<=1) |>
  left_join(ord_pattern, by=join_by(condit,rank,Model,Fit_Method)) |>
  mutate(order_pattern = unlist(order_pattern))

head(combo_pred)
length(unique(combo_pred$order_pattern))

pattern_freq <- combo_pred %>%
  count(order_pattern) %>%
  arrange(desc(n))

# Print the frequency table
print(pattern_freq)

# Plot the frequency distribution
ggplot(pattern_freq, aes(x = order_pattern, y = n)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Frequency Distribution of Order Patterns",
       x = "Order Pattern",
       y = "Frequency")

combo_pred %>% group_by(condit,Model,Fit_Method) |> count(order_pattern) |> arrange(desc(n)) |> ggplot(aes(x = order_pattern, y = n)) +
  geom_bar(stat = "identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(title = "Frequency Distribution of Order Patterns",
       x = "Order Pattern",
       y = "Frequency") +
  ggh4x::facet_nested_wrap(condit~Model)

combo_pred %>%
  group_by(Model, Fit_Method) %>%
  mutate(n_pattern = n_distinct(order_pattern)) %>%
  group_by(Model, Fit_Method, order_pattern) %>%
  mutate(pat_count = n()) %>%
  ungroup() %>%
  group_by(Model, Fit_Method) %>%
  arrange(Model, Fit_Method, desc(pat_count), order_pattern) %>%
  mutate(pat_rank = dense_rank(desc(pat_count))) |> 
  group_by(Model, Fit_Method, order_pattern) %>%
  # distinct(Model, Fit_Method, order_pattern, .keep_all = TRUE) %>%
  # arrange(Model, Fit_Method, pat_rank)
  filter(pat_rank<=5) |>
  filter(condit=="Varied")  |> 
 ggplot(aes(x=c,y=lr,color=as.factor(order_pattern))) + geom_point() + facet_wrap(Fit_Method~Model,scales="free") 
  # use viridis color palette
 # scale_color_viridis_d(option = "magma", direction = -1)

ordered_labels <- ind_ds |>
  group_by(order_pattern, x,condit) |>
  summarize(y = mean(y), n_id = n_distinct(id)) |>
  arrange(-n_id, order_pattern) |>
  mutate(factor_label = paste0(order_pattern, " (n=", n_id, ")")) %>%
  pull(factor_label) %>%
  unique()

k= ind_ds |>
  group_by(order_pattern, x,condit) |>
  summarize(y = mean(y), n_id = n_distinct(id)) |>
  mutate(n_id = factor(n_id, levels = lorder)) |>
  mutate(factor_label = paste0(order_pattern, " (n=", n_id, ")"),
         factor_label = factor(factor_label, levels = ordered_labels))

k |>
  ggplot(aes(x = x, y = y),fill=wes_palette("Darjeeling1")[1]) +
  stat_summary(fun = mean, geom = "bar") +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.25) +
  facet_wrap(~factor_label, scales = "free_x")

k |> filter(condit=="Varied") |>
  ggplot(aes(x = x, y = y,fill=condit),fill=wes_palette("Darjeeling1")[1]) +
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = 0.8)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(width = 0.8), width = 0.25) +
  facet_wrap(~factor_label, scales = "free_x")

k |> filter(condit=="Constant") |>
  ggplot(aes(x = x, y = y),fill=wes_palette("Darjeeling1")[2]) +
  stat_summary(fun = mean, geom = "bar", position = position_dodge(width = 0.8)) +
  stat_summary(fun.data = mean_se, geom = "errorbar", position = position_dodge(width = 0.8), width = 0.25) +
  facet_wrap(~factor_label, scales = "free_x")
